Simplifying Parallel Graph Processing: \\ \large Survey of Existing Platforms

### 2016-12-01 report/survey.tex
Got autogeneration for survey.tex sort of working.
It now only works if you copy the correct csv(s) generated
from graphalytics. Correct means only one dataset was run, but
this may be worked around by running graphalytics multiple times,
copying various files into the "datasets" directory.

% TODO: This should be unnecessary once autogeneration is used.
\begin{table}[!htb]
	\centering
	\begin{tabular}{l|r|r|}
	 & PowerGraph & OpenG \\ \hline
	BFS & 81.8 & 341 \\ \hline
	SSSP & 1.64 & 15.0 \\ \hline
	LCC & 54.6 & 142 \\ \hline
	\end{tabular}
	\caption{Performance Results for the \texttt{dota-league} dataset with 61,670 vertices and 50,870,313 edges. BFS is breadth-first search, SSSP is single-source shortest paths, LCC is local clustering coefficient.}
	\label{tab:perf}
\end{table}

>>>>

% TODO: This should be unnecessary once autogeneration is used.
\begin{table}[!htb]
	\centering
%	\begin{tabular}{l|r|r|}
%	 & PowerGraph & OpenG \\ \hline
%	BFS & 81.8 & 341 \\ \hline
%	SSSP & 1.64 & 15.0 \\ \hline
%	LCC & 54.6 & 142 \\ \hline
%	\end{tabular}

		\centering
		\pgfplotstabletypeset[
			col sep=comma,
			string type, % Makes the .style={string type} redundant
			columns={[index]0,openg,powergraph},
			every head row/.style={after row=\midrule},
			columns/0/.style={string type, column type={l|}, column name={}},
			columns/openg/.style={string type, column type={r}},
			columns/powergraph/.style={string type, column type={r}}
		]{runtime.csv}
	\caption{Performance Results for the \texttt{dota-league} dataset with 61,670 vertices and 50,870,313 edges. BFS is breadth-first search, SSSP is single-source shortest paths, LCC is local clustering coefficient.}
	\label{tab:perf}
\end{table}
